\documentclass[10pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{color}
\usepackage{fontawesome5}

% Color definitions for clean look
\definecolor{darkblue}{rgb}{0.0,0.0,0.5}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,      
    urlcolor=darkblue,
    pdftitle={Adam O'Brien, PhD - Resume},
    pdfpagemode=FullScreen,
}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{8pt}

% Styling definitions
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeHeading}[4]{
  \noindent\textbf{#1} \hfill #2 \\
  \noindent\textit{#3} \hfill \small{#4} \\
  \vspace{2pt}
}

\setlist[itemize]{leftmargin=15pt, label=--}

\begin{document}

\pagestyle{empty}

% Header
\begin{center}
    {\Huge\bfseries Adam O'Brien, PhD} \\
    \vspace{4pt}
    \small
    \faMapMarker*~Mountain View, CA $\cdot$ \faPhone~(603) 266-7012 $\cdot$ \href{mailto:obrienadam89@gmail.com}{\faEnvelope~obrienadam89@gmail.com} \\
    \href{https://github.com/obrienadam}{\faGithub~github.com/obrienadam} $\cdot$ \href{https://www.linkedin.com/in/obrien-adam/}{\faLinkedin~linkedin.com/in/obrien-adam}
\end{center}

\vspace{6pt}

% Summary
\section{Summary}
Software Engineer and Computational Scientist with a PhD in Applied Mathematics and 7+ years of experience designing high-performance computing systems, low-latency runtime components, and massive-scale simulation engines. Experienced in \textbf{JAX/XLA runtime and ML infrastructure} (data pipelines, embedding serving, distributed training at cross-datacenter scale), \textbf{low-latency C++ systems and GPU acceleration} (CUDA, XLA), and large-scale numerical solvers. Proven track record of optimizing core compute infrastructure to drive significant cost savings and throughput increases in production environments.

% Experience
\section{Work Experience}

\resumeHeading{Google LLC}{Sunnyvale, CA}{Software Engineer -- Machine Learning Infrastructure}{Apr. 2023 -- Present}
\begin{itemize}[itemsep=4pt]
    \resumeItem{\textbf{Data Infrastructure (PyGrain \& JAX Data):} Maintain and scale PyGrain and JAX Data, the foundational data pipeline libraries handling ingestion and processing for JAX-based training workloads globally across Google. Designed and built the PyGrain autotuner, a closed-loop online controller using Universal Scalability Law (USL) and Markovian queueing models to dynamically tune worker concurrency, prefetch depth, and batch parameters, significantly reducing the time to build high-performance data pipelines.}
    \resumeItem{\textbf{JAX CPU Embedding Library:} Designed and built Google's high-performance native C++ embedding library from the ground up, featuring cache-optimized embedding table layouts, lock-free lookup structures, and lookup coalescing---delivering 2x--4x throughput improvements over the incumbent TensorFlow-based solution for embedding serving.}
    \resumeItem{\textbf{JAX Parameter Server Training (PST):} Engineered CPU-based distributed training architectures optimized for massive-scale recommendation and ranking models. Optimized parameter server infrastructure to deliver up to a \textbf{3x throughput improvement} in dense worker/server topographies by implementing copy-eliding RPC handlers, custom cache-friendly C++ data structures, and low-overhead threading models. Developed a scalable native C++ optimizer library from scratch with horizontally scalable routines tailored for these topologies, and partnered with cross-functional stakeholders (Ads, YouTube, Play, Geo) to successfully deploy PST into production.}
    \resumeItem{\textbf{Megascale XLA:} Contributed to the Megascale XLA team, implementing topology-aware collective communication primitives within the XLA runtime---including hierarchical tree-based collective planning across intra- and inter-datacenter network tiers---to enable efficient distributed training at cross-metro scale. Received the internal \textbf{``Gold Perfy'' Award} for this contribution.}
\end{itemize}

\vspace{6pt}

\resumeHeading{Aurora Innovation}{Mountain View, CA}{Senior Software Engineer -- Motion Planning Simulation}{Oct. 2021 -- Apr. 2023}
\begin{itemize}[itemsep=4pt]
    \resumeItem{Architected core high-performance software components in C++ for a highly distributed, massive-scale motion planning simulation engine executing hundreds of thousands of autonomous vehicle scenarios daily.}
    \resumeItem{Developed dynamic agent behavior routing frameworks, introducing adversarial interaction profiles and real-time lane-changing mechanics to evaluate safety-critical edge cases.}
    \resumeItem{Created automated validation tools for Foreign Object Debris (FOD) simulations, engineering workflows that dynamically combined real-world sensor logs with synthetic environmental augmentations.}
    \resumeItem{Discovered and executed sweeping runtime optimizations within the mapping and routing engine, generating audited infrastructure savings of \textbf{\textasciitilde\$130,000 per month} in cloud compute expenditures.}
\end{itemize}

\vspace{6pt}

\resumeHeading{Siemens PLM Software}{Lebanon, NH}{Advanced Software Engineer -- Physics Solvers}{Jul. 2019 -- Oct. 2021}
\begin{itemize}[itemsep=4pt]
    \resumeItem{Maintained and optimized parallel fluid dynamics solvers within the flagship industrial simulation suite \textbf{STAR-CCM+}.}
    \resumeItem{Researched and implemented highly parallelized computational methods (\textbf{MPI, OpenMP}) to resolve large-scale, complex partial differential equations on multi-node cluster topographies.}
    \resumeItem{Researched and developed GPU offloading strategies for core Algebraic Multi-Grid (AMG) linear solvers using \textbf{CUDA}.}
\end{itemize}

% Education
\section{Education}
\noindent\textbf{University of Toronto} \hfill Toronto, ON, Canada \\
\textit{PhD in Computational Science / Applied Mathematics} \hfill Sep. 2014 -- Jul. 2019 \\
\vspace{-2pt}
\begin{itemize}[leftmargin=15pt, itemsep=2pt]
    \resumeItem{Thesis: Immersed boundary methods for moving bodies at fluid-fluid-interfaces.}
    \resumeItem{Authored multiple peer-reviewed publications in numerical and computational journals (\textasciitilde 95 academic citations).}
\end{itemize}

% Technical Skills
\section{Technical Skills}
\noindent\textbf{Languages:} C++ (C++11/14/17/20), CUDA, Python, Bash \\
\noindent\textbf{HPC \& ML Infrastructure:} JAX, XLA (Accelerated Linear Algebra), PyGrain, TPU/GPU Hardware Acceleration, MPI, Multi-threading \\
\noindent\textbf{Numerical Software:} PETSc, Trilinos, Eigen, BLAS/LAPACK, HYPRE, NumPy, SciPy

\end{document}
